### 2019-05-01 peer-review/cover-letter.Rmd
added wording changs to draft
added updates for phrasing prior to ubmission

In this paper, we examine a previous analysis of the impact of stopping universal vaccination in England published in the journal of Epidemiology and Community Health in 1989 in light of changing TB epidemiology. Using recent surveillance data, together with modern statistical methods to capture uncertainty, we found that the impact of ending the BCG schools’ scheme was greater than previously estimated. Previous estimates were spuriously precise as parameter uncertainty and measurement error were not fully included. Our work highlights the benefits of reproducibility as our study built on work previously published in this journal.

We believe our manuscript will be of interest to you and the journal’s readership because Bacillus Calmette-Guérin (BCG) is one of the most widely-used vaccines worldwide and our study explores the impact of changing BCG vaccination policy.
We do not have any issues relating to the journal policies. All authors have approved this version of the manuscript for submission and the content of the manuscript has not been published or submitted elsewhere.

>>>>

In this paper, we examine a previous analysis of the impact of stopping universal vaccination in England published in the journal of Epidemiology and Community Health in 1989 in light of changing Tuberculosis epidemiology. Using recent surveillance data, together with modern statistical methods to capture uncertainty, we found that the impact of ending the BCG schools’ scheme was greater than previously estimated. Previous estimates were spuriously precise as parameter uncertainty and measurement error were not fully included. Our work highlights the benefits of reproducibility as our study was built on work previously published in this journal.

We believe our manuscript will be of interest to you and the journal’s readership because Bacillus Calmette-Guérin (BCG) is one of the most widely-used vaccines worldwide and our study explores the impact of changing BCG vaccination policy.

We do not have any issues relating to the journal policies. All authors have approved this version of the manuscript for submission and the content of the manuscript has not been published or submitted elsewhere.
